---
title: "Pins with Quarto"
date: today
date-format: iso
---

The goals of this document are:

- to show how to publish a web-based [pins](https://pins.rstudio.com/) board using Quarto.
- to set up a reprex to ask about best practices for including `resources:` in a Quarto website.

This is motivated by [new capabilities to publish web-based boards](https://github.com/rstudio/pins-r/pull/681) in (the currently-dev version of) pins.

```{r}
#| message: false
library("pins")
library("here")
```

The idea is:

- create a `board_folder()`, write a pin to it, then create a manifest.
- specify the folder as a resource to be included with the published site.

Then, I'll show some code *you* can use to access the data.

## Create board

Normally, I would create just one board. 
However, there's something I'm not quite understanding about how we are meant to use Quarto's `resources:` field, so I'm making an example.

```{r}
board_one <- board_folder(here("data/board_one"), versioned = FALSE)
board_two <- board_folder(here("data/board_two"), versioned = FALSE)
```

For each board, write a pin:

```{r}
board_one |> pin_write(mtcars, "mtcars", type = "json")
```

```{r}
board_two |> pin_write(mtcars, "mtcars", type = "json")
```

For each board, write a manifest:

```{r}
board_one |> write_board_manifest()
board_two |> write_board_manifest()
```

A manifest file will let consumers know about the pins and their versions.

Because the data is published independently from the code, I add `/data/` to the `.gitignore` file.

## Publish board

Here is the `_quarto.yml` file for this project:

```yaml
`r paste(readLines(here("_quarto.yml")), collapse = "\n")`
```

As you can see, I have made a resource entry for each board in different places in the file.

When I render the file, I get a set of warnings:

```
WARNING: File 'data/board_one/mtcars/20221223T162805Z-c2702' was not found.
WARNING: File 'data/board_one/mtcars/20221223T162805Z-c2702/data.txt' was not found.
WARNING: File 'data/board_one/mtcars/20221223T162805Z-c2702/mtcars.json' was not found.
```

The `resources` entry for `data/board_one` results in only the `_pins.yaml` file being copied to `_site`, whereas the entire directory structure for `data/board_two` is copied to `_site`.

In the [site resources documentation](https://quarto.org/docs/websites/website-tools.html#site-resources), it encourages us to put `resources:` within `project:`.

::: {.callout-note}
## Questions

- Is `resources` meant to copy folders recursively?
  - if so, what is the right syntax?
  
- I found the top-level `resources:` by accident.
  Is it meant to act differently from the version in `project:`?
:::

## Consume board

When you publish your Quarto site, for example to GitHub Pages, the board is available as a part of the website.
Anyone can access the data using `board_url()`, like so:

```{r}
board <- board_url("https://ijlyttle.github.io/quarto-pins/data/board_two/")

board |> pin_list()
board |> pin_versions("mtcars")
board |> pin_read("mtcars") |> head()
```

Because the pin above has to be published before it is consumed, we are seeing a previous publication of the pin.
